### 2013-09-04 Tex/chapters/appendix.tex
Kapitel aus Anhang nach vorne verschoben

\subsection{Finite Size Effects at the Example of the Specific Heat}
\label{appendix:finiteSizeEffects}
    In Fig.\ \ref{fig:smeared_out_appendix} the specific heat
    \begin{equation}
        c = \frac{N}{T^2}\avg{\avg{E^2} - \avg{E}^2}
    \end{equation}
    is plotted for different system sizes. The finite size effects are obvious.
    The divergence is finite and gets shallower with smaller \(L\). Besides
    the maximum moves away from the critical temperature with smaller \(L\).
    \begin{figure}[htbp]
        \centering
        \includegraphics[width=0.45\textwidth]{plots/Specific_Heat_0}
        \caption[Finite Size Effects by Example of the Specific Heat]
        {
            Effects of different system sizes on the specific heat \(c\)
            at \(\sigma = 0\). Dotted lines are guides to the eye.
        }
        \label{fig:smeared_out_appendix}
    \end{figure}

\subsection{Course of the Critical Temperature $T_c$ with Fixed Coupling Constants $J$}
\label{appendix:fixedCoupling}
    A quick analysis of this model with fixed coupling constants \(J = 1\)
    (i.e.\ \(\alpha=0\)) is performed. The results are displayed in Fig.\ \ref{fig:Tc_deg_A0}.
    The jump from \(\sigma=0\) to \(\sigma>0\) does not disappear as in Fig.\ \ref{fig:Tc_deg}
    for variable \(J\) with \(\alpha=0.5\). This suggests that the
    disappearance of the jump is a random special case for the function
    \(J_{ij}=e^{\alpha(1-d_{ij})}\) at \(\alpha=0.5\).\\
    The simulations were carried out on \(L \in \{16,32,64\}\) lattices
    for a subset of the \(\sigma\) and \(T\) used in the previous simulation.
    Every other parameter was kept. Also note that the degree \(K\) is
    the same used in \ref{fig:Tc}\subref{sfig:deg:RNG}\subref{sfig:deg:GG}
    because it is obviously independent of \(J\).
    \begin{figure}[htbp]
        \centering
        \subfigure[][]
        {
            \label{sfig:Tc:RNG_A0}
            \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_A0}
        }
        \subfigure[][]
        {
            \label{sfig:Tc:GG_A0}
            \includegraphics[width=0.45\textwidth]{plots/GG_Tc_A0}
        }

        \subfigure[][]
        {
            \label{sfig:Tc_norm_deg:RNG_A0}
            \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_norm_deg_A0}
        }
        \subfigure[][]
        {
            \label{sfig:Tc_norm_deg:GG_A0}
            \includegraphics[width=0.45\textwidth]{plots/GG_Tc_norm_deg_A0}
        }

        \caption[Critical Temperature and Critical Temperature Normalized by Degree of the Graph for Fixed Coupling Constants $J=1$]
        {
            Top: Critical Temperature \(T_c\) of the graph over different
            disorder parameters \(\sigma\) with fixed coupling constants \(J=1\) for
            \subref{sfig:deg:RNG} the RNG and
            \subref{sfig:deg:GG} the GG.\\
            Bottom: Critical temperatures normalized by degree \(K\) over
            different disorder parameters \(\sigma\) with fixed coupling constants \(J=1\) for
            \subref{sfig:Tc_norm_deg:RNG} the RNG and
            \subref{sfig:Tc_norm_deg:GG} the GG.
        }
        \label{fig:Tc_deg_A0}
    \end{figure}\\

>>>>

\subsection{Finite Size Effects at the Example of the Specific Heat}
\label{appendix:finiteSizeEffects}
    In Fig.\ \ref{fig:smeared_out_appendix} the specific heat
    \begin{equation}
        c = \frac{N}{T^2}\avg{\avg{E^2} - \avg{E}^2}
    \end{equation}
    is plotted for different system sizes. The finite size effects are obvious.
    The divergence is finite and gets steeper with larger \(L\). Besides
    the maximum moves to the critical temperature with larger \(L\).
    \begin{figure}[htbp]
        \centering
        \includegraphics[width=0.45\textwidth]{plots/Specific_Heat_0}
        \caption[Finite Size Effects by Example of the Specific Heat]
        {
            Effects of different system sizes on the specific heat \(c\)
            at \(\sigma = 0\). Dotted lines are guides to the eye.
        }
        \label{fig:smeared_out_appendix}
    \end{figure}

### 2013-09-04 Tex/chapters/results.tex
Einrückungsfehler behoben
Kapitel aus Anhang nach vorne verschoben

        this claim in appendix \ref{appendix:fixedCoupling} the same analysis

@@

            \caption[Critical Temperature Normalized by Mean Sum of the Coupling Constants]
            {
                Top: Mean sum of the coupling constants to all
                neighbors over different disorder parameters for
                \subref{sfig:sumJ:RNG} the RNG and
                \subref{sfig:sumJ:GG} the GG.\\
                Bottom: Critical temperatures normalized by mean sum of the
                coupling constants \(\avg{\sum_{\avg{i,j}} J_{ij}}\) over different
                disorder parameters for
                \subref{sfig:Tc_normJ:RNG} the RNG and
                \subref{sfig:Tc_normJ:GG} the GG.
            }
            \label{fig:TcJ}
        \end{figure}\\
        Though Eq.\ \eqref{eq:exactHCTc} shows that there does not have
        to be a linear connection between \(J\) and \(T_c\), the best guess
        is a linear connection, because this model is derived from the
        square lattice, where the connection is linear. Therefore, one
        normalizes \(T_c\) with \(\avg{\sum_{\avg{i,j}} J_{ij}}\) as in
        Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}, the
        jump on the GG arises again, but \(T_c\) is now monotonically
        decreasing with increasing disorder parameter \(\sigma\).
        %~ This is a strong hint, that the change of the \(T_c\) with changing
        %~ \(\sigma\) is in some way connected to \(J\) and \(K\) which is an
        %~ expected conclusion.\\
        Moreover the forms of both curves are quite similar, but the
        one for the RNG in Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}
        is generally lower and spans over a bigger temperature range than
        the curve of the GG in Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:GG}.
        Both graph types have a plateau at \(0 < \sigma < 0.1\). The conclusion
        is that small disorder has little influence on this normalized critical
        temperature.
        Also both graph types exhibit a steep decline after the plateau before
        they approach an asymptotic limit for \(\sigma \gg 1\).\\
        If one looks at the behavior of \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
        for \(\sigma \ll 1\) and consequently \(d_{ij} \approx 1\) the
        following approximation is valid.
        \begin{equation}
            \abs{1-d_{ij}} := \varepsilon \ll 1
        \end{equation}
        \begin{equation}
            J_{ij} = e^{\pm \alpha \varepsilon} \approx 1 \pm \varepsilon \mp \dots
        \end{equation}
        \begin{align}
            \avg{\sum_{\avg{i,j}} J_{ij}} &= \frac{\pm \varepsilon}{N} \avg{\sum_{\avg{i,j}} 1} \\
                                          &= K(1 \pm \varepsilon) \approx K
        \end{align}
        Therefore this normalization is independent of the choice of \(\alpha\)
        at small values of \(\sigma\). In Appendix \ref{appendix:fixedCoupling}
        in Fig.\ \ref{fig:Tc_deg_A0}\subref{sfig:Tc_norm_deg:RNG_A0}\subref{sfig:Tc_norm_deg:GG_A0}
        the values from Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}
        are compared to \(T / K\) for \(\alpha = 0\).

>>>>

        this claim in Sec.\ \ref{appendix:fixedCoupling} the same analysis

@@

            \caption[Critical Temperature Normalized by Mean Sum of the Coupling Constants]
            {
                Top: Mean sum of the coupling constants to all
                neighbors over different disorder parameters for
                \subref{sfig:sumJ:RNG} the RNG and
                \subref{sfig:sumJ:GG} the GG.\\
                Bottom: Critical temperatures normalized by mean sum of the
                coupling constants \(\avg{\sum_{\avg{i,j}} J_{ij}}\) over different
                disorder parameters for
                \subref{sfig:Tc_normJ:RNG} the RNG and
                \subref{sfig:Tc_normJ:GG} the GG.
            }
            \label{fig:TcJ}
        \end{figure}\\
        Though Eq.\ \eqref{eq:exactHCTc} shows that there does not have
        to be a linear connection between \(J\) and \(T_c\), the best guess
        is a linear connection, because this model is derived from the
        square lattice, where the connection is linear. Therefore, one
        normalizes \(T_c\) with \(\avg{\sum_{\avg{i,j}} J_{ij}}\) as in
        Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}, the
        jump on the GG arises again, but \(T_c\) is now monotonically
        decreasing with increasing disorder parameter \(\sigma\).
        %~ This is a strong hint, that the change of the \(T_c\) with changing
        %~ \(\sigma\) is in some way connected to \(J\) and \(K\) which is an
        %~ expected conclusion.\\
        Moreover the forms of both curves are quite similar, but the
        one for the RNG in Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}
        is generally lower and spans over a bigger temperature range than
        the curve of the GG in Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:GG}.
        Both graph types have a plateau at \(0 < \sigma < 0.1\). The conclusion
        is that small disorder has little influence on this normalized critical
        temperature.
        Also both graph types exhibit a steep decline after the plateau before
        they approach an asymptotic limit for \(\sigma \gg 1\).\\
        If one looks at the behavior of \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
        for \(\sigma \ll 1\) and consequently \(d_{ij} \approx 1\) the
        following approximation is valid.
        \begin{equation}
            \abs{1-d_{ij}} := \varepsilon \ll 1
        \end{equation}
        \begin{equation}
            J_{ij} = e^{\pm \alpha \varepsilon} \approx 1 \pm \varepsilon \mp \dots
        \end{equation}
        \begin{align}
            \avg{\sum_{\avg{i,j}} J_{ij}} &= \frac{\pm \varepsilon}{N} \avg{\sum_{\avg{i,j}} 1} \\
                                          &= K(1 \pm \varepsilon) \approx K
        \end{align}
        Therefore this normalization is independent of the choice of \(\alpha\)
        at small values of \(\sigma\). In Sec.\ \ref{appendix:fixedCoupling}
        in Fig.\ \ref{fig:Tc_deg_A0}\subref{sfig:Tc_norm_deg:RNG_A0}\subref{sfig:Tc_norm_deg:GG_A0}
        the values from Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}
        are compared to \(T / K\) for \(\alpha = 0\).

    \subsection{Course of the Critical Temperature $T_c$ with Fixed Coupling Constants $J$}
    \label{appendix:fixedCoupling}
        A quick analysis of this model with fixed coupling constants \(J = 1\)
        (i.e.\ \(\alpha=0\)) is performed. The results are displayed in Fig.\ \ref{fig:Tc_deg_A0}.
        The jump from \(\sigma=0\) to \(\sigma>0\) does not disappear as in Fig.\ \ref{fig:Tc_deg}
        for variable \(J\) with \(\alpha=0.5\). This suggests that the
        disappearance of the jump is a random special case for the function
        \(J_{ij}=e^{\alpha(1-d_{ij})}\) at \(\alpha=0.5\).\\
        The simulations were carried out on \(L \in \{16,32,64\}\) lattices
        for a subset of the \(\sigma\) and \(T\) used in the previous simulation.
        Also note that the degree \(K\) is
        the same used in \ref{fig:Tc}\subref{sfig:deg:RNG}\subref{sfig:deg:GG}
        because it is obviously independent of \(J\).
        Further, note that for small values of \(\sigma < 0.3\), \(T_c / K\)
        obtained using the fixed coupling strength \(J=1\) coincides with
        \(T_c / \avg{\sum_{\avg{i,j}}J_{ij}}\) obtained using the distance
        dependent coupling strength, Eq.\ \ref{eq:coupling}.
        This can be expected from the approximate analytic statement presented
        in Sec.\ \ref{sssec:J}.
        \begin{figure}[htbp]
            \centering
            \subfigure[][]
            {
                \label{sfig:Tc:RNG_A0}
                \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_A0}
            }
            \subfigure[][]
            {
                \label{sfig:Tc:GG_A0}
                \includegraphics[width=0.45\textwidth]{plots/GG_Tc_A0}
            }

            \subfigure[][]
            {
                \label{sfig:Tc_norm_deg:RNG_A0}
                \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_norm_deg_A0}
            }
            \subfigure[][]
            {
                \label{sfig:Tc_norm_deg:GG_A0}
                \includegraphics[width=0.45\textwidth]{plots/GG_Tc_norm_deg_A0}
            }

            \caption[Critical Temperature and Critical Temperature Normalized by Degree of the Graph for Fixed Coupling Constants $J=1$]
            {
                Top: Critical Temperature \(T_c\) of the graph over different
                disorder parameters \(\sigma\) with fixed coupling constants \(J=1\) for
                \subref{sfig:deg:RNG} the RNG and
                \subref{sfig:deg:GG} the GG.\\
                Bottom: Critical temperatures normalized by degree \(K\) over
                different disorder parameters \(\sigma\) with fixed coupling constants \(J=1\) for
                \subref{sfig:Tc_norm_deg:RNG} the RNG and
                \subref{sfig:Tc_norm_deg:GG} the GG. The values of \(T_c / K\)
                are compared to those of \(T_c /  \avg{\sum_{\avg{i,j}}J_{ij}}\)
                from Sec.\ \ref{sssec:J}.
            }
            \label{fig:Tc_deg_A0}
        \end{figure}
